Included  Summary (teaching-v2.0)

### 2021-06-19 experiment-2/analysis/preprocessor/included_summary.Rmd
corrected trimming (don't remove SubNr 2)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Design
- Each performance (1 trial) contains 72 responses for onsets and 72 responses for offsets (i.e., if there is no mistake, 144 responses in total)
- Each block contains 8 trials and there are 4 blocks (teaching vs. performing x articulation vs. dynamics)
- Note: SubNr 3 was excluded due to insufficient motor skills. SubNr 2 was excluded due to a deviated tempo.

@@

### Export only included participants
data_analysis~.txt are used for data analysis.
```{r export-csv, echo = TRUE}
fwrite(dt_ioi[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_ioi.txt", sep = ",")
fwrite(dt_kor[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_kor.txt", sep = ",")
fwrite(dt_kot[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_kot.txt", sep = ",")
fwrite(dt_vel[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_vel.txt", sep = ",")
fwrite(dt_vel_diff[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_vel_diff.txt", sep = ",")
```

>>>>

# Design
- Each performance (1 trial) contains 72 responses for onsets and 72 responses for offsets (i.e., if there is no mistake, 144 responses in total)
- Each block contains 8 trials and there are 4 blocks (teaching vs. performing x articulation vs. dynamics)
- Note: SubNr 3 was excluded due to insufficient motor skills.

@@

### Export only included participants
data_analysis~.txt are used for data analysis.
```{r export-csv, echo = TRUE}
fwrite(dt_ioi[SubNr != 3], file = "./trimmed/data_analysis_ioi.txt", sep = ",")
fwrite(dt_kor[SubNr != 3], file = "./trimmed/data_analysis_kor.txt", sep = ",")
fwrite(dt_kot[SubNr != 3], file = "./trimmed/data_analysis_kot.txt", sep = ",")
fwrite(dt_vel[SubNr != 3], file = "./trimmed/data_analysis_vel.txt", sep = ",")
fwrite(dt_vel_diff[SubNr != 3], file = "./trimmed/data_analysis_vel_diff.txt", sep = ",")
```
